Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
修改细节
修改数学符号错误

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target (see Figure \ref{fig:net}).
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.

\begin{algorithm}[tb]
\caption{Training Process}
\label{alg:algorithm}
\textbf{Input}: Training dataset $\mathcal{V}$, Siamese tracker $T$, max iteration $N$\\
\textbf{Output}: Universal perturbation $\delta$ and universal patch $p$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $i = 0$.
\WHILE{$i < N$}
\STATE Random pick a video $V\in \mathcal{V}$. The corresponding ground truth is $B^{gt}=\{b^{gt}_i\}^T_i$.
\STATE Random pick two frames $I_t, I_s$ from $v$.
\STATE Generate template image $\textbf{z}$ according to $I_t$ and $b^{gt}_t$.
\STATE $\tilde z = z + \delta$
\STATE Generate search image $\textbf{x}$ according to $I_s$ and $b^{gt}_s$.
\STATE Calculate the fake target position $\{l^x, l^y, w, h\}$ relative to the search image.
\STATE $\tilde{\textbf x} = A(\textbf x, p_i, (l^x, l^y), (w, h)).$
\STATE $\textbf{C, R, Q} = \phi(\tilde {\textbf x}, \tilde{\textbf z}).$
\STATE Generate fake labels $\textbf{C}^*,\textbf{R}^*,\textbf{Q}^*$ using $\{l^x, l^y, w, h\}$.
\STATE Calculate loss $L(\textbf{C, R, Q}, \textbf{C}^*, \textbf{R}^*, \textbf{Q}^*)$ using Equ. \ref{eq:loss}.
\STATE $delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)$
\STATE $p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L)$
\STATE $i = i + 1$
\ENDWHILE
\STATE \textbf{return} $\delta_N, p_N.$
\end{algorithmic}
\end{algorithm}

@@

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers.
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with an offset $(\Delta_x, \Delta_y)$. We set this offset to $(\pm 64, \pm 64)$. The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_i, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.

@@

The loss function is calculated as follows:
\begin{equation}
\begin{array}{l}
\begin{aligned}
L&=\frac{\alpha}{N_{\mathrm{pos}}} \sum_{x, y} L_{\mathrm{cls}}\left(\textbf{C}_{x, y}, \textbf{C}_{x, y}^{*}\right) \\
&+\frac{\beta}{N_{\mathrm{pos}}} \sum_{x, y} \textbf{1}_{\left\{\textbf{C}_{x, y}^{*}>0\right\}} L_{\mathrm{quality}}\left(\textbf{Q}_{x, y}, \textbf{Q}_{x, y}^{*}\right) \\
&+\frac{\gamma}{N_{\mathrm{pos}}} \sum_{x, y} \textbf{1}_{\left\{\textbf{C}_{x, y}^{*}>0\right\}} L_{\mathrm{reg}}\left(\textbf{R}_{x, y}, \textbf{R}_{x, y}^{*}\right) \\
&+\eta \cdot ||\delta||_2^2 +  \sigma \cdot ||p||^2_2
\end{aligned}
\end{array}
\label{eq:loss}
\end{equation}
\textcolor{black} %(SiamFC++)
{where $\textbf{C}_{x, y}, \textbf{R}_{x, y}, \textbf{Q}_{x, y}$ represent the values of $\textbf{C}, \textbf{R}, \textbf{Q}$ at location $(x, y)$, respectively. $\textbf{C}^*, \textbf{R}^*, \textbf{Q}^*$ are the fake labels generated according to the position/size of the fake target.$\textbf 1$ is the indicator function that takes 1 if the condition in subscribe holds and takes 0 if not, $L_{\mathrm{cls}}$ denote the focal loss for classification result, $L_{\mathrm{quality}}$ denote the binary cross entropy (BCE) loss for quality assessment and $L_{\mathrm{reg}}$ denote the IoU loss \cite{iou-loss} for bounding box result. Following SiamFC++, we assign 1 to $\textbf{C}_{x, y}^{*}$ if $(x, y)$ is considered as a positive sample, and 0 if as a negative sample.}

@@

Once the perturbations $(\delta, p)$ is trained, we can use them to perturb the template image and search images of any natural video. Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require solving an optimisation problem/gradient computation.
Assume $B^{fake}=\{b^{fake}_i\}_1^{T}$ is the trajectory we hope the tracker to output.
During tracking the $i$-th frame of the video $V=\{I_i\}_1^T$, we need to transform the bounding box $b^{fake}_i$ (relative to the original frame $I_i$) into the box $\hat b_i=\{l^x_i, l^y_i, w_i, h_i\}$ relative to the search image $\textbf x_i$, and paste $p$ into $\textbf x_i$ according to $\hat b_i$:
\begin{equation}
\tilde{\textbf x}_i = A(\textbf x_i, p, (l^x_i, l^y_i), (w_i, h_i)).
\end{equation}
The tracker then takes $\tilde{\textbf z}=\textbf z+\delta$ and $\tilde{ \textbf x}_i$ as input, and the subsequent tracking procedure remains the same as SiamFC++.

>>>>

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target (see Figure \ref{fig:net}).
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require gradient optimisation or network inference.

\begin{algorithm}[tb]
\caption{Training Process}
\label{alg:algorithm}
\textbf{Input}: Training dataset $\mathcal{V}$, Siamese tracker $T$, max iteration $N$\\
\textbf{Output}: Universal perturbation $\delta$ and universal patch $p$.
\begin{algorithmic}[1] %[1] enables line numbers
\STATE Let $i = 0$.
\WHILE{$i < N$}
\STATE Random pick a video $V\in \mathcal{V}$. The corresponding ground truth is $B^{gt}=\{b^{gt}_i\}^T_i$.
\STATE Random pick two frames $I_t, I_s$ from $v$.
\STATE Generate template image $\textbf{z}$ according to $I_t$ and $b^{gt}_t$.
\STATE $\tilde z = z + \delta$
\STATE Generate search image $\textbf{x}$ according to $I_s$ and $b^{gt}_s$.
\STATE Calculate the fake target position $\{l^x, l^y, w, h\}$ relative to the search image.
\STATE $\tilde{\textbf x} = A(\textbf x, p_i, (l^x, l^y), (w, h)).$
\STATE $\textbf{C, R, Q} = \phi(\tilde {\textbf x}, \tilde{\textbf z}).$
\STATE Generate fake labels $\textbf{C}^*,\textbf{R}^*,\textbf{Q}^*$ using $\{l^x, l^y, w, h\}$.
\STATE Calculate loss $L(\textbf{C, R, Q}, \textbf{C}^*, \textbf{R}^*, \textbf{Q}^*)$ using Equ. \ref{eq:loss}.
\STATE $\delta_{k+1} = \delta_{k} - \epsilon_1 \cdot \text{sign}(\nabla_{\delta_k}L)$
\STATE $p_{k+1} = p_{k} - \epsilon_2 \cdot \text{sign}(\nabla_{p_k}L)$
\STATE $i = i + 1$
\ENDWHILE
\STATE \textbf{return} $\delta_N, p_N.$
\end{algorithmic}
\end{algorithm}

@@

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers.
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with a shift of 64 pixels, where shift is defined as the max range of translation generated by a uniform distribution.
%an offset $(\Delta_x, \Delta_y)$.
%We set this offset to $(\pm 64, \pm 64)$. 
%$\Delta_x$ (as well as $\Delta_y$) is randomly selected between -64 pixels and 64 pixels.
The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.

@@

The loss function is calculated as follows:
\begin{equation}
\begin{array}{l}
\begin{aligned}
L&=\frac{\alpha}{N_{\mathrm{pos}}} \sum_{x, y} L_{\mathrm{cls}}\left(\textbf{C}_{x, y}, \textbf{C}_{x, y}^{*}\right) \\
&+\frac{\beta}{N_{\mathrm{pos}}} \sum_{x, y} \textbf{1}_{\left\{\textbf{C}_{x, y}^{*}>0\right\}} L_{\mathrm{quality}}\left(\textbf{Q}_{x, y}, \textbf{Q}_{x, y}^{*}\right) \\
&+\frac{\gamma}{N_{\mathrm{pos}}} \sum_{x, y} \textbf{1}_{\left\{\textbf{C}_{x, y}^{*}>0\right\}} L_{\mathrm{reg}}\left(\textbf{R}_{x, y}, \textbf{R}_{x, y}^{*}\right) \\
&+\eta \cdot ||\delta_k||_2^2 +  \sigma \cdot ||p_k||^2_2
\end{aligned}
\end{array}
\label{eq:loss}
\end{equation}
\textcolor{black} %(SiamFC++)
{where $\textbf{C}_{x, y}, \textbf{R}_{x, y}, \textbf{Q}_{x, y}$ represent the values of $\textbf{C}, \textbf{R}, \textbf{Q}$ at location $(x, y)$, respectively. $\textbf{C}^*, \textbf{R}^*, \textbf{Q}^*$ are the fake labels generated according to the position/size of the fake target.$\textbf 1$ is the indicator function that takes 1 if the condition in subscribe holds and takes 0 if not, $L_{\mathrm{cls}}$ denote the focal loss for classification result, $L_{\mathrm{quality}}$ denote the binary cross entropy (BCE) loss for quality assessment and $L_{\mathrm{reg}}$ denote the IoU loss \cite{iou-loss} for bounding box result. Following SiamFC++, we assign 1 to $\textbf{C}_{x, y}^{*}$ if $(x, y)$ is considered as a positive sample, and 0 if as a negative sample.}

@@

Once the perturbations $(\delta, p)$ is trained, we can use them to perturb the template image and search images of any natural video. Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require gradient optimisation or network inference.
Assume $B^{fake}=\{b^{fake}_i\}_1^{T}$ is the trajectory we hope the tracker to output.
During tracking the $i$-th frame of the video $V=\{I_i\}_1^T$, we need to transform the bounding box $b^{fake}_i$ (relative to the original frame $I_i$) into the box $\hat b_i=\{l^x_i, l^y_i, w_i, h_i\}$ relative to the search image $\textbf x_i$, and paste $p$ into $\textbf x_i$ according to $\hat b_i$:
\begin{equation}
\tilde{\textbf x}_i = A(\textbf x_i, p, (l^x_i, l^y_i), (w_i, h_i)).
\end{equation}
The tracker then takes $\tilde{\textbf z}_i=\textbf z_i+\delta$ and $\tilde{ \textbf x}_i$ as input, and the subsequent tracking procedure remains the same as SiamFC++.
